# Distance {.unnumbered}

The Euclidian distance between successive tree-visits, in units of pixels.

```{r setup, include=FALSE}
source("_libraries.R")
source("_prettify.R")
source("_plot_preferences.R")
knitr::opts_chunk$set(fig.path='e1_figures/')
knitr::opts_chunk$set(fig.width=7, fig.height=5)
options(dplyr.summarise.inform=F)
```

## E1 Distance - Prepare the data

Read the data and pre-process it.

```{r e1_ntrees_prep_data}
e1 <- readRDS("001-00-e1-data.RDS")

# remove things from the raw data to make it 
# suitable for this particular analysis

# remove samples that did not look at a tree
e1 <- e1 %>% filter(fl>0)

# remove the second (and any subsequent) *consecutive* duplicates
e1 <- e1 %>% 
  group_by(pp, rr, tb) %>% 
  filter(is.na(tl != lag(tl)) | tl != lag(tl)) %>% 
  ungroup()

# remove trials where they failed to get 10 fruit
e1 <- e1 %>% 
  group_by(pp, rr, tb) %>% 
  mutate(max_fr = max(fr)) %>% 
  ungroup() %>% 
  filter(max_fr==10)

# Euclid
e1 <- e1 %>% 
  group_by(pp, rr, tb) %>% 
  mutate(dist = round(sqrt((lead(xx)-xx)^2 + (lead(yy)-yy)^2), 2)) %>% 
  ungroup()

# time
e1 <- e1 %>% 
  group_by(pp, rr, tb) %>% 
  mutate(tm=tm-first(tm)) %>%
  ungroup()

# fewer columns
e1 <- e1 %>% 
  select(pp, rr, st, tb, tm, ll, tl, dist)

e1 <- e1 %>% 
  mutate(pp = as_factor(pp), 
         st=as_factor(st), 
         tb=as_factor(tb),
         ll=factor(ll, levels=c("fruit", "not"), labels=c(
           "Launched from fruit", "Launched from tree without fruit"
         )),
         rr=factor(rr, levels=c("dispersed", "patchy")), 
         )


#2 x 2 x 2
#launch x resources x stage


dst <- e1 %>% 
  group_by(pp, rr, st, ll, tb) %>% 
  # average over tree-visits yielding
  # two values for each trial, 
  # one for launch from fruit, 
  # one for launch from empty
  summarise(dist=mean(dist, na.rm=TRUE)) %>% 
  arrange(pp, rr, st, ll, tb, .by_group = TRUE) %>% 
  ungroup()

# average over trials in each of the two stages,
# to yield one row for each launch type, per stage
# 8 rows per subject, 2 x 2 x 2
# 2 x 2 x 2 x 42=336 rows
dst <- dst %>% 
  group_by(pp, rr, st, ll) %>% 
  summarise(mu.dist=mean(dist, na.rm=TRUE)) %>% 
  ungroup()


dst <- dst %>% 
  select(rr, st, ll, pp, mu.dist) %>% 
  arrange(rr, st, ll, pp, mu.dist)

saveRDS(dst, "e1_distance_data.rds")
```

## E1 Distance ANOVA

Run the ANOVA

2 x 2 x 2 
resources, stage, launch

```{r e1-distance-aov}
options(contrasts=c("contr.sum","contr.poly"))
e1_distance_ANOVA <- 
  ezANOVA(data=dst,
          dv=mu.dist,
          wid=pp,
          within=c(rr, st, ll),
          type=3, 
          return_aov = TRUE)
if("Sphericity Corrections" %in% names(e1_distance_ANOVA)){
  corr=aovSphericityAdjustment(e1_distance_ANOVA)$ANOVA %>% tibble()
} else {
  corr=e1_distance_ANOVA$ANOVA %>% tibble()  
  }
```

Table the ANOVA

```{r}
prettify_anova(e1_distance_ANOVA, "E1 Distance ANOVA")
```

Report the ANOVA

The effect of resources was 
F(`r round(corr[corr$Effect=="rr","DFn"],1)`, 
  `r round(corr[corr$Effect=="rr","DFd"],1)`) = 
  `r round(corr[corr$Effect=="rr", "F"],2)`, 
  `r case_when(
    corr[corr$Effect=="rr","p"] <.001 ~ "p<.001",
    corr[corr$Effect=="rr","p"] <.01  ~ "p<.01",
    corr[corr$Effect=="rr","p"] <.05  ~ "p<.05",
    TRUE ~ paste0("p=",format(round(pull(corr[corr$Effect=="rr","p"]),3), scientific = F, nsmall=3)))`.

The effect of stage was 
F(`r round(corr[corr$Effect=="st","DFn"],1)`, 
  `r round(corr[corr$Effect=="st","DFd"],1)`) = 
  `r round(corr[corr$Effect=="st", "F"],2)`, 
  `r case_when(
    corr[corr$Effect=="st","p"] <.001 ~ "p<.001",
    corr[corr$Effect=="st","p"] <.01  ~ "p<.01",
    corr[corr$Effect=="st","p"] <.05  ~ "p<.05",
    TRUE ~ paste0("p=",format(round(pull(corr[corr$Effect=="st","p"]),3), scientific = F, nsmall=3)))`.
    
The effect of stage was 
F(`r round(corr[corr$Effect=="ll","DFn"],1)`, 
  `r round(corr[corr$Effect=="ll","DFd"],1)`) = 
  `r round(corr[corr$Effect=="ll", "F"],2)`, 
  `r case_when(
    corr[corr$Effect=="ll","p"] <.001 ~ "p<.001",
    corr[corr$Effect=="ll","p"] <.01  ~ "p<.01",
    corr[corr$Effect=="ll","p"] <.05  ~ "p<.05",
    TRUE ~ paste0("p=",format(round(pull(corr[corr$Effect=="ll","p"]),3), scientific = F, nsmall=3)))`.
    
The effect of the interaction resources x stage x launch was 
F(`r round(corr[corr$Effect=="rr:st:ll","DFn"],1)`, 
  `r round(corr[corr$Effect=="rr:st:ll","DFd"],1)`) = 
  `r round(corr[corr$Effect=="rr:st:ll", "F"],2)`, 
  `r case_when(
    corr[corr$Effect=="rr:st:ll","p"] <.001 ~ "p<.001",
    corr[corr$Effect=="rr:st:ll","p"] <.01  ~ "p<.01",
    corr[corr$Effect=="rr:st:ll","p"] <.05  ~ "p<.05",
    TRUE ~ paste0("p=",format(round(pull(corr[corr$Effect=="rr:st:ll","p"]),3), scientific = F, nsmall=3)))`.
    
    