#  Revisits  {.unnumbered}

This number is how many trees they pointlessly looked at again after already getting the fruit - it corresponds with memory errors.

```{r setup, include=FALSE}
source("_libraries.R")
source("_prettify.R")
source("_plot_preferences.R")
knitr::opts_chunk$set(fig.path='e1_figures/')
knitr::opts_chunk$set(fig.width=7, fig.height=5)
options(dplyr.summarise.inform=F)
```

## E1 Revisits: Prepare the data

Read in the data and pre-process it.

```{r e1_revisits_prep_data}
e1 <- readRDS("001-00-e1-data.RDS")

# remove things from the raw data to make it 
# suitable for this particular analysis

# remove samples that did not look at a tree
e1 <- e1 %>% filter(fl>0)

# remove the second (and any subsequent) *consecutive* duplicates
e1 <- e1 %>% 
  group_by(pp, rr, tb) %>% 
  filter(is.na(tl != lag(tl)) | tl != lag(tl)) %>% 
  ungroup()

# remove trials where they failed to get 10 fruit
e1 <- e1 %>%
  group_by(pp, rr, tb) %>%
  mutate(max_fr = max(fr)) %>%
  ungroup() %>%
  filter(max_fr==10) %>% 
  select(-c(ex, max_fr, te, tt, st, xx, yy, ll))

# currently some trials don't have entries for fruit of zero
# these trials are where they found a fruit on the first tree
# We want to say that these were:
# number of revisits = 0 
# (not number of revisits = "a structural missing")
design <-
  tibble(
    expand.grid(
      pp=unique(e1$pp),
      rr=unique(e1$rr),
      tb=unique(e1$tb),
      fr=0
    )
  )
e1 <- 
  full_join(x=design, y=e1, by = join_by(pp, rr, tb, fr)) %>% 
  group_by(pp, rr, tb) %>% 
  arrange(pp, rr, tb, fr, tm, .by_group = TRUE) %>% 
  replace_na(list(ix=0, tm=0, tl=0, fl=-1)) %>% 
  ungroup()

# annotate with revisit
e1 <- e1 %>% 
  group_by(pp, rr, tb) %>% 
  mutate(isrv = duplicated(tl)) %>% 
  ungroup()  

# get number of revisits per fruit
# (is how many times they looked at a tree that 
#  they saw before on this trial on the way to 
#  getting this particular fruit)
e1 <- e1 %>% 
  select(pp, rr, tb, fr, isrv) %>% 
  group_by(pp, rr, tb, fr) %>% 
  summarise(nrv=sum(isrv)) %>% 
  ungroup()

# add the stage IV
e1 <- e1 %>% 
  mutate(
    st = ifelse(tb<=5, "early", "late")
  ) %>% 
  select(pp,rr, st, tb, fr, nrv)

# factors
e1 <- e1 %>% 
  mutate(pp=as_factor(pp), rr=as_factor(rr), st=as_factor(st)) %>% 
  ungroup()

# collapse over trials - what was the average number of revisits for this fruit,
# now that the absence of visits to trees while fr was zero contributes a zero
# not a structural missing. Also prune entries for fr == 10 which are all 
# constrained to be zero
nrev_data_for_aov <- e1 %>% 
  group_by(pp, rr, st, fr) %>% 
  summarise(nrv=mean(nrv)) %>% 
  filter(fr!=10) %>% 
  mutate(fr=as_factor(fr)) %>% 
  ungroup()

# collapse over trials to stages
nrev_data_for_ggplot <- nrev_data_for_aov %>% 
  group_by(pp, rr, st) %>% 
  summarise(nrv=mean(nrv)) %>% 
  ungroup()

saveRDS(nrev_data_for_ggplot, "e1_nrevisits_plot_data.rds")
```

## E1 Revisits: ANOVA

2 * 2 * 10

A 2x2x10 ANOVA with the within factors resource distribution (patchy, dispersed) and trial (early [mean trials 1-5], late [mean trials 6-10]) and number of fruit consumed (1-10) 

Run the ANOVA

```{r e1_revisits_anova}
options(contrasts=c("contr.sum","contr.poly"))
e1_revisits_ANOVA <- 
  ezANOVA(data=nrev_data_for_aov,
          dv=nrv,
          wid=pp,
          within=c(rr, st, fr),
          type=3, 
          return_aov = TRUE)
if("Sphericity Corrections" %in% names(e1_revisits_ANOVA)){
  corr=aovSphericityAdjustment(e1_revisits_ANOVA)$ANOVA %>% tibble()
} else {
  corr=e1_revisits_ANOVA$ANOVA %>% tibble()  
  }
```

Table the ANOVA.

```{r e1_nrevisits_print_anova_table}
prettify_sphericity_3_way(
  aovSphericityAdjustment(e1_revisits_ANOVA), 
  "E1 NRevisits ANOVA")
```

Report the ANOVA

The effect of resources was 
F(`r round(corr[corr$Effect=="rr","DFn"],1)`, 
  `r round(corr[corr$Effect=="rr","DFd"],1)`) = 
  `r round(corr[corr$Effect=="rr", "F"],2)`, 
  `r case_when(
    corr[corr$Effect=="rr","p"] <.001 ~ "p<.001",
    corr[corr$Effect=="rr","p"] <.01  ~ "p<.01",
    corr[corr$Effect=="rr","p"] <.05  ~ "p<.05",
    TRUE ~ paste0("p=",format(round(pull(corr[corr$Effect=="rr","p"]),3), scientific = F, nsmall=3)))`.

The effect of stage was 
F(`r round(corr[corr$Effect=="st","DFn"],1)`, 
  `r round(corr[corr$Effect=="st","DFd"],1)`) = 
  `r round(corr[corr$Effect=="st", "F"],2)`, 
  `r case_when(
    corr[corr$Effect=="st","p"] <.001 ~ "p<.001",
    corr[corr$Effect=="st","p"] <.01  ~ "p<.01",
    corr[corr$Effect=="st","p"] <.05  ~ "p<.05",
    TRUE ~ paste0("p=",format(round(pull(corr[corr$Effect=="st","p"]),3), scientific = F, nsmall=3)))`.

The effect of fruit was 
F(`r round(corr[corr$Effect=="fr","DFn"],1)`, 
  `r round(corr[corr$Effect=="fr","DFd"],1)`) = 
  `r round(corr[corr$Effect=="fr", "F"],2)`, 
  `r case_when(
    corr[corr$Effect=="fr","p"] <.001 ~ "p<.001",
    corr[corr$Effect=="fr","p"] <.01  ~ "p<.01",
    corr[corr$Effect=="fr","p"] <.05  ~ "p<.05",
    TRUE ~ paste0("p=",format(round(pull(corr[corr$Effect=="fr","p"]),3), scientific = F, nsmall=3)))`.

The fruit x resources interaction was 
F(`r round(corr[corr$Effect=="rr:fr","DFn"],1)`, 
  `r round(corr[corr$Effect=="rr:fr","DFd"],1)`) = 
  `r round(corr[corr$Effect=="rr:fr", "F"],2)`, 
  `r case_when(
    corr[corr$Effect=="rr:fr","p"] <.001 ~ "p<.001",
    corr[corr$Effect=="rr:fr","p"] <.01  ~ "p<.01",
    corr[corr$Effect=="rr:fr","p"] <.05  ~ "p<.05",
    TRUE ~ paste0("p=",format(round(pull(corr[corr$Effect=="rr:fr","p"]),3), scientific = F, nsmall=3)))`.

## E1 NRevisits: Plot

Two points along the x axis, each participant contributes one point per cell

```{r e1_nrevisits_plot}
ggplot(data=nrev_data_for_ggplot, aes(y=nrv, x=st, group=rr, shape=rr, fill=rr)
) +
  my_fgms_theme+
  ggtitle("(b): Revisits (memory errors)")+
  ylab("Revisits")+
  xlab("Trials")+
  scale_fill_manual(name="Resource\ndistribution",values=c("white", "black")) +
  scale_shape_manual(name="Resource\ndistribution",values=c(24,19)) +
  stat_summary(fun.data = mean_cl_normal, geom = "errorbar", width=0.1, position=pd) +
  stat_summary(fun = mean, geom = "line", position=pd) + 
  stat_summary(fun = mean, geom = "point", size=4, position=pd)+
  scale_x_discrete(labels=c("early\ntrials 1 to 5", "late\ntrials 6 to 10"))
```

## E1 NRevisits: Stage means

Table means for stage

```{r e1_nrevisits_stage_means}
frpremeans = nrev_data_for_ggplot %>% group_by(st, pp, rr) %>%
  summarise(mu=mean(nrv)) %>% 
  summarise(mu=mean(mu))  
frmeans <- frpremeans %>% 
  summarise(mean=mean(mu), sd=sd(mu))
prettify_means(frmeans, "E1 NRevisits stage means")
```

## E1 NRevisits: Fruit means

```{r e1_nrevisits_fruit_means}
pre.means = nrev_data_for_aov %>% 
  group_by(fr, pp, st) %>% 
  # average over resources
  summarise(mean.nrv=mean(nrv)) %>% 
  group_by(fr, pp) %>% 
  # average over stage
  summarise(mean.nrv=mean(mean.nrv))
ok.means = pre.means %>% 
  group_by(fr) %>% 
  summarise(mean=mean(mean.nrv), sd=sd(mean.nrv))
prettify_means(ok.means, "E1 Nrevisits fruit means")
```







