# Trees {.unnumbered}

This number is how many trees they looked at overall to get the fourteen out of fifteen fruit - high numbers represent worse performance.

```{r setup, include=FALSE}
source("_libraries.R")
source("_prettify.R")
source("_plot_preferences.R")
knitr::opts_chunk$set(fig.path='e2_figures/')
knitr::opts_chunk$set(fig.width=7, fig.height=5)
options(dplyr.summarise.inform=F)
```

## E2 Ntrees: Prepare the data

Read the data in and pre-process it.

```{r e2_ntrees_prep_data}
e2 <- readRDS("002-00-e2-data.RDS")

# remove things from the raw data to make it 
# suitable for this particular analysis

# remove samples that did not look at a tree
e2 <- e2 %>% filter(fl>0)

# remove the second (and any subsequent) *consecutive* duplicates
e2 <- e2 %>% 
  group_by(ff, pp, rr, tb) %>% 
  filter(is.na(tl != lag(tl)) | tl != lag(tl)) %>% 
  ungroup()

# remove trials where they failed to get 14 fruit
e2 <- e2 %>% 
  group_by(ff, pp, rr, tb) %>% 
  mutate(max_fr = max(fr)) %>% 
  ungroup() %>% 
  filter(max_fr==14)

# average over tree-visits to get counts for each trial
ntr.counts <- e2 %>% 
  select(ff, pp, rr, st, tb, tl) %>% 
  group_by(ff, pp, rr, st, tb) %>% 
  summarise(ntrees=n()) %>% 
  ungroup() %>% 
  mutate(ff=as_factor(ff), pp=as_factor(pp), rr=as_factor(rr),  st=as_factor(st))

# average over trials to get mean count for each stage
ntr <- ntr.counts %>% 
  group_by(ff, pp, rr, st) %>% 
  summarise(mean_ntrees_per_stage=mean(ntrees)) %>% 
  ungroup()

saveRDS(ntr, "e2_ntrees_plot_data.rds")
```

## E2 Ntrees: ANOVA

Run the ANOVA

```{r e2_ntrees_ANOVA}
options(contrasts=c("contr.sum","contr.poly"))
e2_ntrees_ANOVA <- 
  ezANOVA(data=ntr,
          dv=mean_ntrees_per_stage,
          wid=pp,
          within=c(rr, st),
          between=ff,
          type=3,
          return_aov = TRUE)
if("Sphericity Corrections" %in% names(e2_ntrees_ANOVA)){
  corr=aovSphericityAdjustment(e2_ntrees_ANOVA)$ANOVA %>% tibble()
} else {
  corr=e2_ntrees_ANOVA$ANOVA %>% tibble()  
  }
```

Do we care about unbalanced anova? There were `r unique(ntr %>% filter(ff=="fade")) %>% pull(pp) %>% unique() %>% length()` subjects in fade but `r unique(ntr %>% filter(ff=="no_fade")) %>% pull(pp) %>% unique() %>% length()` in no_fade.


Table the ANOVA. 

```{r e2_ntrees_print_anova_table}
prettify_anova(e2_ntrees_ANOVA, "e2 Ntrees ANOVA")
```

Report the anova

### Main effects

The effect of fading was 
F(`r round(corr[corr$Effect=="ff","DFn"],1)`, 
  `r round(corr[corr$Effect=="ff","DFd"],1)`) = 
  `r round(corr[corr$Effect=="ff", "F"],2)`, 
  `r case_when(
    corr[corr$Effect=="ff","p"] <.001 ~ "p<.001",
    corr[corr$Effect=="ff","p"] <.01  ~ "p<.01",
    corr[corr$Effect=="ff","p"] <.05  ~ "p<.05",
    TRUE ~ paste0("p=",format(round(pull(corr[corr$Effect=="ff","p"]),3), scientific = F, nsmall=3)))`.


The effect of resources was 
F(`r round(corr[corr$Effect=="rr","DFn"],1)`, 
  `r round(corr[corr$Effect=="rr","DFd"],1)`) = 
  `r round(corr[corr$Effect=="rr", "F"],2)`, 
  `r case_when(
    corr[corr$Effect=="rr","p"] <.001 ~ "p<.001",
    corr[corr$Effect=="rr","p"] <.01  ~ "p<.01",
    corr[corr$Effect=="rr","p"] <.05  ~ "p<.05",
    TRUE ~ paste0("p=",format(round(pull(corr[corr$Effect=="rr","p"]),3), scientific = F, nsmall=3)))`.


The effect of stage was 
F(`r round(corr[corr$Effect=="st","DFn"],1)`, 
  `r round(corr[corr$Effect=="st","DFd"],1)`) = 
  `r round(corr[corr$Effect=="st", "F"],2)`, 
  `r case_when(
    corr[corr$Effect=="st","p"] <.001 ~ "p<.001",
    corr[corr$Effect=="st","p"] <.01  ~ "p<.01",
    corr[corr$Effect=="st","p"] <.05  ~ "p<.05",
    TRUE ~ paste0("p=",format(round(pull(corr[corr$Effect=="st","p"]),3), scientific = F, nsmall=3)))`.

### Two-way interactions  

The effect of fading x stage was 
F(`r round(corr[corr$Effect=="ff:st","DFn"],1)`, 
  `r round(corr[corr$Effect=="ff:st","DFd"],1)`) = 
  `r round(corr[corr$Effect=="ff:st", "F"],2)`, 
  `r case_when(
    corr[corr$Effect=="ff:st","p"] <.001 ~ "p<.001",
    corr[corr$Effect=="ff:st","p"] <.01  ~ "p<.01",
    corr[corr$Effect=="ff:st","p"] <.05  ~ "p<.05",
    TRUE ~ paste0("p=",format(round(pull(corr[corr$Effect=="ff:st","p"]),3), scientific = F, nsmall=3)))`.

The effect of resources x stage was 
F(`r round(corr[corr$Effect=="rr:st","DFn"],1)`, 
  `r round(corr[corr$Effect=="rr:st","DFd"],1)`) = 
  `r round(corr[corr$Effect=="rr:st", "F"],2)`, 
  `r case_when(
    corr[corr$Effect=="rr:st","p"] <.001 ~ "p<.001",
    corr[corr$Effect=="rr:st","p"] <.01  ~ "p<.01",
    corr[corr$Effect=="rr:st","p"] <.05  ~ "p<.05",
    TRUE ~ paste0("p=",format(round(pull(corr[corr$Effect=="rr:st","p"]),3), scientific = F, nsmall=3)))`.
    
## plots

```{r, e2_ntrees_plot}
ggplot(data=ntr, aes(x=st, y=mean_ntrees_per_stage, group=rr, fill=rr, shape=rr)) + 
  #facet_wrap(~ff) +
  ggtitle("(a): Total trees visited")+
  ylab("Visits")+
  xlab("Trials")+
  my_fgms_theme+  
  scale_fill_manual(name="Resource\ndistribution",values=c("white", "black")) +
  scale_shape_manual(name="Resource\ndistribution",values=c(24,19)) +
  stat_summary(fun.data = mean_cl_normal, geom = "errorbar", width=0.1, position=pd) +
  stat_summary(fun = mean, geom = "line", position=pd) + 
  stat_summary(fun = mean, geom = "point", size=3, position=pd)+
  scale_x_discrete(labels=c("early trials\n1 to 10", "late trials\n11 to 20"))
```

## Means

Table means for resources

```{r e2_Number_of_trees_resources_means}
rrpremeans = ntr %>% group_by(rr, pp, st) %>%
  summarise(mu=mean(mean_ntrees_per_stage)) %>% 
  summarise(mu=mean(mu)) 
rrmeans <- rrpremeans %>% 
  summarise(mean=mean(mu), sd=sd(mu))
prettify_means(rrmeans, "E2 Number of trees resources means")
```

Table means for stage

```{r e2_Number of trees_fruit_means}
frpremeans = ntr %>% group_by(st, pp, rr) %>%
  summarise(mu=mean(mean_ntrees_per_stage)) %>% 
  summarise(mu=mean(mu))  
frmeans <- frpremeans %>% 
  summarise(mean=mean(mu), sd=sd(mu))
prettify_means(frmeans, "E2 Number of trees stage means")
```

